Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

A remark is in order about duplicate removal. A result tuple of Type 2 can belong to, in the worst case, all the $4(k-2)$ sub-types. Hence, by considering each sub-type separately, we may see the same result tuple multiple times (precisely, up to $4(k-2)$ times) in the whole algorithm. However, this does {\em not} mean that the tuple need to be {\em reported} multiple times. Whenever a Type-2 result tuple is found, we can immediately decide all the sub-types it belongs to. To avoid outputting the tuple more than once, we can enforce a policy to designate a specific sub-type for outputting. One such policy is the following: among all sub-types that the tuple belongs to, identify the one with the smallest sub-type number $t$ (an integer from 1 to $4(k-2)$); report the tuple only when we are computing the particular sub-type $t$.

>>>>

A remark is in order about duplicate removal. A result tuple of Type 2 can belong to, in the worst case, all the $4(k-2)$ sub-types. Hence, by considering each sub-type separately, we may see the same result tuple multiple times (precisely, up to $4(k-2)$ times) in the whole algorithm. However, this does {\em not} mean that the tuple needs to be {\em reported} multiple times. Whenever a Type-2 result tuple is found, we can immediately decide in $O(k)$ time all the sub-types it belongs to. To avoid outputting the tuple more than once, we can enforce a policy to designate a specific sub-type for outputting. One such policy is the following: among all sub-types that the tuple belongs to, identify the one with the smallest sub-type number $t$ (an integer from 1 to $4(k-2)$); report the tuple only when we are computing the particular sub-type $t$.
